\bf Forecasts Reconciliation: A geometric view with new insights on bias correction.

### 2019-07-18 Hierarchical-forecast-reconciliation/HierarchicalForecastReconciliation.tex

	In this section we discuss two sensible properties that can be achieved by reconciliation via orthogonal projection.  The  first is that reconciliation should adjust the base forecasts as little as possible, i.e. the base and reconciled forecast should be `close'.  The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realisation that is the target of the forecast.

	To address the first of these properties we make the concept of closeness more concrete, by considering the Euclidean distance between the base forecast $\hat{\bm{y}}$ and the reconciled forecast  $\tilde{\bm{y}}$.  A property of an orthogonal projection is that the distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ will be as small as possible while still ensuring that $\tilde{\bm{y}}\in\mathfrak{s}$.  In this sense reconciliation via orthogonal projection leads to the smallest possible adjustments of the base forecasts.

@@

	\begin{theo}[Distance reducing property]\label{th:distred}
		If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection onto $\mathfrak{s}$, then the following inequality holds:
		\begin{equation}
		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|^2_2.
		\end{equation}
	\end{theo}
	\begin{proof}
		Since the aggregation constraints must hold for all realisations, $\bm{y}_{t+h}\in\mathfrak{s}$ and $\bm{y}_{t+h}=\bm{S}\bm{G}\bm{y}_{t+h}$ since $\bm{S}\bm{G}$ is a projection onto $\mathfrak{s}$. Therefore,
		\begin{align}
		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2&=\|(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\bm{y}_{t+h})\|_2\\
		&=\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
		\end{align}
		The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators \citep{Hun2001}, therefore
		\begin{equation*}
		\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\le
		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
		\end{equation*}
	\end{proof}
	The inequality is strict whenever $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$.

@@

	The simple geometric intuition behind the proof is demonstrated in Figure~\ref{fig:Schematic_OLSRecon}.  In this schematic, the coherent subspace is depicted as a black arrow.  The base forecast $\hat{\bm{y}}$ is shown as a blue dot.  Since it is incoherent it does not lie in $\mathfrak{s}$.  Reconciliation is an orthogonal projection from $\hat{\bm{y}}$ to the coherent subspace yielding the reconciled forecast $\tilde{\bm{y}}$ shown in red.  Finally, the target of the forecast $\bm{y}$ is displayed as a black point, and although its exact location is unknown to the forecaster, it is known that it will lie somewhere along the coherent subspace.

@@

	Figure~\ref{fig:Schematic_OLSRecon} clearly shows that $\hat{\bm{y}}$, $\tilde{\bm{y}}$ and $\bm{y}$ form a right angled triangle.  In this triangle the distance between $\bm{y}$ and $\hat{\bm{y}}$ is the hypotenuse and therefore must be longer than the distance between $\bm{y}$ and $\tilde{\bm{y}}$.  As such reconciliation is guaranteed to reduce the squared error of the forecast.

    Theorem~\ref{th:distred} is in some ways more powerful than perhaps previously understood.  It is often stated in terms of expectations\todo{check other proofs}.  However, the distance reducing property result is even stronger since it will hold for any realisation and any forecast.  Nothing needs to be assumed about the statistical properties of the data generating process or the process by which forecasts are made.  
    f
    However, in other ways, Theorem~\ref{th:distred} is weaker than perhaps often understood. First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy.  In particular, this measure is the root of the sum of squared errors of {\em all} variables in the hierarchy.  As such, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to worse forecasts for individual series. Second, although orthogonal projections are guaranteed to improve on base forecasts both for all realisations and in expectation, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy.  As such referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections, in particular MinT. It is to oblique projections that we now turn our attention.

@@

	Another way of understanding the generalised Euclidean geometry is that it is defined by the norm $\bm{v}'\bm{W}^{1}\bm{v}$.  This interpretation is quite instructive when it comes to thinking about the connection between distances and loss functions.  In the generalised Euclidean geometry, the distance between the reconciled forecast and the realisation is given by $(\hat{\bm{y}}-\bm{y})'\bm{W}^{-1}(\hat{\bm{y}}-\bm{y})$.  For diagonal $\bm{W}$ this is equivalent to a weighted sum of squared error loss function and when $\bm{W}$ is a covariance matrix this is equivalent to a Mahalanobis distance.  As such Theorem~\ref{th:distred} can easily be generalised.  If the objective function is some weighted sum of squared errors, or a Mahalanobis distance, then the projection matrix $\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts, for an appropriately selected $\bm{W}$.

@@

	Figure~\ref{fig:MinT_justification1} provides geometrical intuition into the MinT method.  Suppose the in-sample errors are given by the orange points.  They provide information on the most likely direction of large deviations from the coherent subspace.  This direction is denoted by $\bm{R}$.  Figure~\ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts.  One such forecast is depicted in blue as $\hat{\bm{y}}$.  An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection.  Imagining a similar oblique projection along $\bm{R}$ for all the grey points yield reconciled forecasts tightly packed near the target $\bm{y}$.  In this sense, the oblique MinT projection minimises the forecast error variance of reconciled forecasts.\todo{needs picture with all points projected obliquely then orthogonally}.

@@

	The property that projections map all vectors in the coherent subspace onto themselves is useful in proving the unbiasedness preserving property of reconciliation \todo{reference Shanika and maybe van Erven Culigari}.  Before restating this proof using a  clear geometric interpretation we discuss in a precise fashion what is meant by unbiasedness.

	Suppose that the target of a point forecast is $\bm{\mu}_{t+h|t}:=\E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$ where the expectation is taken over the predictive density.  Our point forecast can be thought of as an estimate of this quantity.  The forecast is random due to uncertainty in the training sample and it is with respect to this uncertainty that unbiasedness refers.  More concretely, the point forecast will be unbiased if $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\bm{\mu}_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.

@@

	Finally, it is often stated that an assumption required to prove the unbiasedness preserving property is that $\bm{SGS}=\bm{S}$ or alternatively that $\bm{GS}=\bm{I}$.  Both of these conditions are equivalent to assuming that $\bm{SG}$ is a projection matrix.  \todo{perhaps elaborate in a proof in appendix}  However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{GS}=\bm{I}$. This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ is an unconstrained manner.  However, equipped with a geometric understanding of the problem, we would advise against this approach.  Dropping the constraint is not just about bias $\bm{GS}=\bm{I}$ but rather moves away projections and all of their attractive properties.  Our own solution to dealing with biased forecasts is to bias correct, or translate the forecast prior to reconciling via projections.  It is to this approach that we now turn our attention.

@@

>>>>

	In this section we discuss two sensible properties that can be achieved by reconciliation via orthogonal projection.  The  first is that reconciliation should adjust the base forecasts as little as possible, i.e. the base and reconciled forecast should be `close'.  The second is that reconciliation in some sense should improve forecast accuracy, or more loosely, that the reconciled forecast should be `closer' to the realised value that is targeted by the forecast.

	To address the first of these properties we make the concept of closeness more concrete, by considering the Euclidean distance between the base forecast $\hat{\bm{y}}$ and the reconciled forecast  $\tilde{\bm{y}}$.  A property of an orthogonal projection is that the distance between $\hat{\bm{y}}$ and $\tilde{\bm{y}}$ is minimal for over any possible $\tilde{\bm{y}}\in\mathfrak{s}$.  In this sense reconciliation via orthogonal projection leads to the smallest possible adjustments of the base forecasts.

@@

	\begin{theo}[Distance reducing property]\label{th:distred}
		If $\tilde{\bm{y}}_{t+h|t}=\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}$, where $\bm{G}$ is such that $\bm{S}\bm{G}$ is an orthogonal projection onto $\mathfrak{s}$, then the following inequality holds:
		\begin{equation}
		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\le\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
		\end{equation}
	\end{theo}
	\begin{proof}
		Since the aggregation constraints must hold for all realisations, $\bm{y}_{t+h}\in\mathfrak{s}$ and $\bm{y}_{t+h}=\bm{S}\bm{G}\bm{y}_{t+h}$ since $\bm{S}\bm{G}$ is a projection onto $\mathfrak{s}$. Therefore,
		\begin{align}
		\|(\tilde{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2&=\|(\bm{S}\bm{G}\hat{\bm{y}}_{t+h|t}-\bm{S}\bm{G}\bm{y}_{t+h})\|_2\\
		&=\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
		\end{align}
		The Cauchy-Schwarz inequality can be used to show that orthogonal projections are bounded operators \citep{Hun2001}, therefore
		\begin{equation*}
		\|\bm{S}\bm{G}(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2\le
		\|(\hat{\bm{y}}_{t+h|t}-\bm{y}_{t+h})\|_2.
		\end{equation*}
	\end{proof}
	The inequality is strict whenever $\hat{\bm{y}}_{t+h|t}\notin\mathfrak{s}$.

@@

	The simple geometric intuition behind the proof is demonstrated in Figure~\ref{fig:Schematic_OLSRecon}.  In this schematic, the coherent subspace is depicted as a black arrow.  The base forecast $\hat{\bm{y}}$ is shown as a blue dot.  Since $\hat{\bm{y}}$ is incoherent it does not lie in $\mathfrak{s}$.  Reconciliation is an orthogonal projection from $\hat{\bm{y}}$ to the coherent subspace yielding the reconciled forecast $\tilde{\bm{y}}$ shown in red.  Finally, the target of the forecast $\bm{y}$ is displayed as a black point, and although its exact location is unknown to the forecaster, it is known that it will lie somewhere along the coherent subspace.

@@

	Figure~\ref{fig:Schematic_OLSRecon} clearly shows that $\hat{\bm{y}}$, $\tilde{\bm{y}}$ and $\bm{y}$ form a right angled triangle with $\tilde{y}$ at the right-angled vertex.  In this triangle the line between $\bm{y}$ and $\hat{\bm{y}}$ is the hypotenuse and therefore must be longer than the distance between $\bm{y}$ and $\tilde{\bm{y}}$.  As such reconciliation is guaranteed to reduce the squared error of the forecast. \todo{Do we just include this as the proof rather than the existing proof to 3.1}

    Theorem~\ref{th:distred} is in some ways more powerful than perhaps previously understood.  It is often stated in terms of expectations\todo{check other proofs}.  However, the distance reducing property will hold for any realisation and any forecast and not just on average.  Nothing needs to be assumed about the statistical properties of the data generating process or the process by which forecasts are made.

    However, in other ways, Theorem~\ref{th:distred} is weaker than perhaps often understood. First, when improvements in forecast accuracy are discussed in the context of the theorem, this refers to a very specific measure of forecast accuracy.  In particular, this measure is the root of the sum of squared errors of {\em all} variables in the hierarchy.  As such, while forecast improvement is guaranteed for the hierarchy overall, reconciliation can lead to worse forecasts for individual series. Second, although orthogonal projections are guaranteed to improve on base forecasts, they are not necessarily the projection that leads to the greatest improvement in forecast accuracy.  As such referring to reconciliation via orthogonal projections as `optimal' is somewhat misleading since it does not have the optimality properties of some oblique projections, in particular MinT. It is to oblique projections that we now turn our attention.

@@

	Another way of understanding the generalised Euclidean geometry is that it is defined by the norm $\bm{v}'\bm{W}^{-1}\bm{v}$.  This interpretation is quite instructive when it comes to thinking about the connection between distances and loss functions.  In the generalised Euclidean geometry, the distance between the reconciled forecast and the realisation is given by $(\hat{\bm{y}}-\bm{y})'\bm{W}^{-1}(\hat{\bm{y}}-\bm{y})$.  For diagonal $\bm{W}$ this is equivalent to a weighted sum of squared error loss function and when $\bm{W}$ is a covariance matrix this is equivalent to a Mahalanobis distance.  As such Theorem~\ref{th:distred} can easily be generalised.  If the objective function is some weighted sum of squared errors, or a Mahalanobis distance, then the projection matrix $\bm{S}\left(\bm{S}'\bm{W}^{-1}\bm{S}\right)^{-1}\bm{S}'\bm{W}^{-1}$ is guaranteed to improve forecast accuracy over base forecasts, for an appropriately selected $\bm{W}$.

@@

	Figure~\ref{fig:MinT_justification1} provides geometrical intuition into the MinT method.  Suppose the in-sample errors are given by the orange points.  They provide information on the most likely direction of large deviations from the coherent subspace.  This direction is denoted by $\bm{R}$.  Figure~\ref{fig:MinT_justification2} then shows a target value of $\bm{y}$, while the grey points indicate possible values for the base forecasts (the base forecasts are of course stochastic).  One possible value of the forecast is depicted in blue as $\hat{\bm{y}}$.  An oblique projection of the blue point back along the direction of $\bm{R}$ yields a reconciled forecast closer to the target, especially compared to an orthogonal projection.  Imagining a similar oblique projection along $\bm{R}$ for all the grey points yield reconciled forecasts tightly packed near the target $\bm{y}$.  In this sense, the oblique MinT projection minimises the forecast error variance of reconciled forecasts.\todo{needs picture with all points projected obliquely then orthogonally}.

@@

	The property that projections map all vectors in the coherent subspace onto themselves is also useful in proving the unbiasedness preserving property of reconciliation \todo{reference Shanika and maybe van Erven Culigari}.  Before restating this proof using a  clear geometric interpretation we discuss in a precise fashion what is meant by unbiasedness.

	Suppose that the target of a point forecast is $\bm{\mu}_{t+h|t}:=\E(\bm{y}_{t+h}\mid\bm{y}_{1},\dots,\bm{y}_{t})$ where the expectation is taken over the predictive density.  Our point forecast can be thought of as an estimate of this quantity.\todo{or do we want to define unbiasedness of a forecast as the expected value of the forecast equals realisation?}  The forecast is random due to uncertainty in the training sample and it is with respect to this uncertainty that unbiasedness refers.  More concretely, the point forecast will be unbiased if $\E_{1:t}(\hat{\bm{y}}_{t+h|t})=\bm{\mu}_{t+h|t}$, where the subscript $1:t$ denotes an expectation taken over the training sample.

@@

	Finally, it is often stated that an assumption required to prove the unbiasedness preserving property is that $\bm{SGS}=\bm{S}$ or alternatively that $\bm{GS}=\bm{I}$.  Both of these conditions are equivalent to assuming that $\bm{SG}$ is a projection matrix.  \todo{perhaps elaborate in a proof in appendix}  However, problems arise when viewing the preservation of unbiasedness through the prism of imposing a constraint $\bm{GS}=\bm{I}$. This thinking suggests that a way to deal with biased forecasts is to select $\bm{G}$ in an unconstrained manner.  However, equipped with a geometric understanding of the problem, we would advise against this approach.  The constraint $\bm{GS}=\bm{I}$  is not just about bias and dropping the constraint compromises all of the attractive properties of projections.  Our own solution to dealing with biased forecasts is to bias correct, or translate the forecast prior to reconciling via projections.  It is to this approach that we now turn our attention.

@@

	Our approach to bias correction is to simply estimate the bias by taking the sample mean of $\bm{y_{t+h}}-\hat{\bm{y}_{t+h|t}}$ for all $t+h$ in the training sample.  This can be then subtracted from future forecasts.  As stated in the discussion of MinT, in-sample errors are already used to estimate the optimal direction of projection.  As such we see no problems with using the same errors to bias correct.  Geometrically, the intuition is simple.  In Figure~\ref{fig:MinT_justification1}, the orange points are centered around the origin as would be expected from an unbiased forecast.  If forecasts are biased, then errors should simply be translated until they are centered at the origin.
